Figures to insert in text

### 2018-03-02 Chapters/sdm-applications.tex
Minor changes
sdm + bibtex

In the learning phase, noisy images are generated and they are written into SDM chunked with their labels. The chunk was calculated using the exclusive or (XOR) operator. So, the image bitstring was written to the address of its bitstrings XOR its label bitstring --- \pyth{write(addr=bs_image ^ bs_label, datum=bs_image)}.

>>>>

In the learning phase, noisy images are generated and they are written into SDM chunked with their labels. The chunk was calculated using the exclusive or (XOR) operator. So, the image bitstring was written to the address of its bitstrings XOR its label bitstring --- write($addr=bs_{image} XOR bs_{label}, datum=bs_{image}$).

### 2018-03-02 Chapters/sdm2.tex
sdm + bibtex

\begin{figure}[p!]
  \centering
  \subfloat[]{\includegraphics[width=2.2in]{./images02/new-images/qn3.png}}
  \subfloat[]{\includegraphics[width=2.2in]{./images02/new-images/qn7.png}}

  \subfloat[]{\includegraphics[width=4.0in]{./images02/new-images/qn10.png}}
  \caption{Graph $Q_n$, for $n \in$ \{3, 7, 10\}. Each node represents a possible bitstring in $\{0,1\}^n$, and two nodes are linked if the bitstrings differ by a single dimension.  A number of observations can be made here. First, the number of nodes grows as $2^n$ as $n$ grows; which makes use of the entire space infeasible as $n>>20$. Another interesting observation, better seen in the figures below, is that most of the space lies at the center, at a distance of around 500 from any given vantage point. Though Kanerva has derived many combinatorial properties of the space, I believe that this is a aesthetically appealing object on its own, and beautiful results can be found in the graph-theoretical literature.\label{hypercubes}}
\end{figure}

%FOOTNOTE:

@@

%  (See \cite{@article{harary1988survey,
%    title={A survey of the theory of hypercube graphs},
%    author={Harary, Frank and Hayes, John P and Wu, Horng-Jyh},
%    journal={Computers \& Mathematics with Applications},
%    volume={15},
%    number={4},
%    pages={277--289},
%    year={1988},
%    publisher={Elsevier}
%  }}

>>>>

\begin{figure}[p!]
  \centering
  \subfloat[$Q_3$]{\includegraphics[width=2.2in]{./images02/new-images/qn3.png}}
  \subfloat[$Q_7$]{\includegraphics[width=2.2in]{./images02/new-images/qn7.png}}

  \subfloat[$Q_{10}$]{\includegraphics[width=4.0in]{./images02/new-images/qn10.png}}
  \caption{Here we have $Q_n$, for $n \in$ \{3, 7, 10\}. Each node represents a possible bitstring in $\{0,1\}^n$, and two nodes are linked if the bitstrings differ by a single dimension.  A number of observations can be made here. First, the number of nodes grows as $2^n$ as $n$ grows; which makes use of the entire space infeasible as $n>>20$. Another interesting observation, better seen in the figures below, is that most of the space lies at the center, at a distance of around 500 from any given vantage point. Though Kanerva has derived many combinatorial properties of the space, I believe that this is a aesthetically appealing object on its own, and beautiful results can be found in the graph-theoretical literature.\label{hypercubes}}
\end{figure}

%FOOTNOTE:
The graph composed of $\{0,1\}^n$ nodes and links between nodes $iff$ their Hamming distance is one is called the \emph{hypercube graph}, or $Q_n$.  It is a beautiful combinatorial object on its own for which one can find a survey in \citet{harary1988survey}.

@@
